---
title: "R4DS Chapter 16 Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}

library(learnr)

library(gradethis)

tutorial_options(exercise.checker = gradethis::grade_learnr)

knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)

library(nycflights13)
library(lubridate)

```



## Chapter 16

### 16.1 Easy HD 


*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("How many days are there in a leap year?",
    answer("363"),
    answer("364"),
    answer("366", correct = TRUE),
    answer("367")
  )
)
```


### 16.2.1 Intermediate HD


Use the appropriate lubridate function to parse the following date and time
 "2000-Oct-21 04:00:00"

```{r 16_2_1_Intermediate_NGUYEN, exercise=TRUE, exercise.eval=TRUE}

```

```{r 16_2_1_Intermediate_NGUYEN-hint}
ymd_hms("2000-Oct-21 04:00:00")
```

### 16.2.1 Intermediate HD
Add a function to supplying the UTC timezone for ymd(20170131) in order to force the creation of a date-time from a date
```{r 16_2_1_1_Intermediate_NGUYEN, exercise=TRUE, exercise.eval=TRUE}

```

```{r 16_2_1_1_Intermediate_NGUYEN-hint}
ymd(20170131, tz = "UTC")
```

### 16.2.2 Challenging HD
Write the function that outputs the departure date & time of the flights dataset using make_datetime()
```{r 16_2_2_Challenging_NGUYEN, exercise=TRUE, exercise.eval=TRUE}

```

```{r 16_2_2_Challenging_NGUYEN-hint}
flights %>%
select(year, month, day, hour, minute) %>%
mutate(departure = make_datetime(year, month, day, hour, minute))
```

### 16.2.3 Easy HD
Using as_datetime, write the function that outputs "1970-01-01 5:00:00 UTC"
```{r 16_2_3_Easy_NGUYEN, exercise=TRUE, exercise.eval=TRUE}

```

```{r 16_2_3_Easy_NGUYEN-hint}
as_datetime(60 * 60 * 5)
```









