---
title: "Tidyverse Tutorial: R4DS Ch 16"
output: 
  learnr::tutorial:
    css: css/style.css
    theme: cerulean
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
tutorial_options(exercise.checker = gradethis::grade_learnr)
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(nycflights13)
```


###### This tutorial was written by the following students at Ritsumeikan Asia Pacific University in Japan as part of a seminar project under the supervision of Prof. William Claster. To collaborate please contact us.

-Satoshi OTSU (S.O)


####### Do as many of the exercises as you like
## Section 16.2

### 16.2.4 Easy S.O

*After reading the chapter which one of the following was descripe during the introducting of Date and Time.*

Fill in all of the following that was described.

```{r quiz_16_2_4_Easy}
quiz(
  question("which of the following was asked at the start of the chapter?",
    answer("Does every year have 365 days?", correct = TRUE),
    answer("Does every day have 24 hours?", correct = TRUE),
    answer("Does every minute have 60 seconds?", correct = TRUE),
    answer("Does every hour have 60 minutes?")
  )
)
```

### 16.2.4 Easy S.O

*Modify the following code to the current date.*

```{r 1, exercise=TRUE, exercise.eval=TRUE}
ymd(20220126)
```
```{r 1-hint-1}
"ymd means year, month, and date."

```

### 16.2.4 Intermediate S.O 

```{r Q3-interm-SO}
flights %>% 
     select(year, month, day, hour, minute) %>% 
     mutate(departure = make_datetime(year, month, day, hour, minute))
```


Enter the code that creates the following data.

```{r Q3, exercise=TRUE}

```

```{r Q3-solution}
flights %>% 
+     select(year, month, day, hour, minute) %>% 
+     mutate(departure = make_datetime(year, month, day, hour, minute))
```

### 16.2.4 Intermediate S.O 

Question to verify that one has understood how to use codes for date and time.

```{r 2-4interquiz-SO}
quiz(
  question("Which of the following is applicable in creating date/time and date-times:",
    answer("make_date()", correct = TRUE),
    answer("make_datetime()", correct = TRUE),
    answer("make_timedate()"),
    answer("make_time()")
  )
)
```

### 16.2.4 Challenging S.O

*Try making the following answer with the code you learned.*

[1] "1970-01-01 10:00:00 UTC"

```{r Q5, exercise=TRUE}

```

```{r Q5-solution}
as_datetime(60 * 60 * 10)
```

