---
title: "Tidyverse Tutorial: R4DS Ch 16"
output: 
  learnr::tutorial:
    css: css/style.css
    theme: cerulean
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
tutorial_options(exercise.checker = gradethis::grade_learnr)
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(nycflights13)
```


###### This tutorial was written by the following students at Ritsumeikan Asia Pacific University in Japan as part of a seminar project under the supervision of Prof. William Claster. To collaborate please contact us.

-Satoshi OTSU (S.O)


####### Do as many of the exercises as you like
## Section 16

### 16.1 Easy S.O

*After reading the chapter please answer the following question.*

Fill in the correct answer

```{r quiz_16_1_Easy}
quiz(
  question("In every year there are 365 days.",
    answer("True"),
    answer("False", correct = TRUE)
  )
)
```

### 16.2.1 Easy SO

*Modify the following code to the date of 2022 of March the 2nd.*

```{r 16-2-1EasySO, exercise=TRUE, exercise.eval=TRUE}
ymd(20220126)
```

```{r 16-2-1EasySO-hint}
ymd stands for year, month, and date. 
```

```{r 16-2-1EasySO-solution}
ymd(20220302)
```


### 16.2.2 Intermediate S.O 


```{r 16-2-2GraphSO}
flights %>% 
     select(year, month, day, hour, minute) %>% 
     mutate(departure = make_datetime(year, month, day, hour, minute))
```


Enter the code that creates the following data including the pipe operator.

```{r 16-2-2intermediateSO, exercise=TRUE}
  
```

```{r 16-2-2intermediateSO-hint}
The pipe operator will look like this when written 
flights %>% 
     select() %>% 

```


```{r 16-2-2intermediateSO-solution}
flights %>% 
     select(year, month, day, hour, minute) %>% 
     mutate(departure = make_datetime(year, month, day, hour, minute))
```

### 16.2.3 Intermediate S.O 

Question to verify that one has understood how to use codes for date and time.

```{r 16-2-3intermediatequizSO}
quiz(
  question("Which of the following is applicable in creating date/time and date-times:",
    answer("make_date()", correct = TRUE),
    answer("make_datetime()", correct = TRUE),
    answer("make_timedate()"),
    answer("make_time()")
  )
)
```

### 16.2.4 Challenging S.O

*How do we get date/times as numeric offsets from the “Unix Epoch”, 1970-01-01. If the offset is in seconds?*

```{r 16-2-4ChallengingSO, exercise=TRUE}

```

```{r 16-2-4ChallengingSO-hint}
as_datetime(60 * __ * __)
```

```{r 16-2-4ChallengingSO-solution}
as_datetime(60 * 60 * 10)
```

