---
title: "Tidyverse Tutorial: R4DS Ch 16"
output: learnr::tutorial
runtime: shiny_prerendered
theme: cerulean
style: css/style.css
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Tidyverse Tutorial: R4DS Ch 16

### Easy 16.1.1 OT

```{r quiz1}
quiz(
  question("What are the packages you need to run this tutorial?",
    answer("tidyverse", correct = TRUE),
    answer("learnr"),
    answer("nycflights13", correct = TRUE),
    answer("lubridate", correct = TRUE)
  )
)
```

### Easy 16.2.1 OT

Refer to flights data set. Filter the data to show only the flights in January

```{r filter-jan, exercise=TRUE}
flights %>% 
  filter()
```


### Intermediate 16.2.2 OT

Make a new column that says the name of the month instead of the number:

```{r mutate-month, exercise=TRUE}
flights %>% 
  mutate(month_name = )
```

### Intermediate 16.2.3 OT

Count how many flights per year and month

```{r count-flights, exercise=TRUE}
flights %>%
  group_by() %>%
  summarise(count = )
```

### Challenging 16.2.4 OT

Arrange the flight's distance from the origin to the destination from the furthest to the closest

```{r distance-flights, exercise=TRUE}
flights %>%

```
### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

